The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-25 doc/articles/amsi_biotissue/paper.tex
modifying latex packages used to compiler paper, need to use 'pdflatex --shell-escape' in order for the eps figures to be converted to pdf, just add a .bash_profile alias for pdflatex to save the hastle

\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{url}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

@@

\section{Introduction}\label{introduction}
[Need a couple sentences to talk about how multi-scale is important]
Implementation of multi-scale numerical simulations typically rely on either an ad-hoc set of algorithms designed for a particular problem, or on large frameworks and runtimes. 
Ad-hoc approaches, by their nature, are targeted to a particular multi-scale problem for a specific set of single-scale numerical codes, and thus offer no wider utility beyond their immediate usage as a simulation code.
Framework and runtime approaches are more flexible and admit a broader range of reuse, but typically necessitate that single-scale operations be adapted to work in the ecosystem they create.

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage{listings}
%\usepackage{mathtools}
\usepackage{url}
%\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

@@

\section{Introduction}\label{introduction}
[Need a couple sentences to talk about how multi-scale is important]

Implementation of multi-scale numerical simulations typically rely on either an ad-hoc set of algorithms designed for a particular problem, or on large frameworks and runtimes.
Ad-hoc approaches, by their nature, are targeted to a particular multi-scale problem for a specific set of single-scale numerical codes, and thus offer no wider utility beyond their immediate usage as a simulation code.
Framework and runtime approaches are more flexible and admit a broader range of reuse, but typically necessitate that single-scale operations be adapted to work in the ecosystem they create.
